Ideal model selection is impossible

### 2014-10-27 Facticity/Facticity/paper.tex
...

\newcommand{\sdr}[1]{\textcolor{blue}{\small #1\textsuperscript{[sdr]} }}
\newcommand{\pb}[1]{\textcolor{OliveGreen}{\small #1 \textsuperscript{[pb]} }}

@@

@@

\noindent \pb{Ik denk dat we dit kunnen bewijzen, maar het leidt uiteindelijk maar tot een logterm variantie tussen verschillende versies van G. Dat betekent dat ze asymptotisch niet echt verschillen. Wat we nodig hebben is een groot model $f$ waarvan we weten dat er een $x$ in $B^n$ zit, die met $f$ $C(x)$ to op een constant benaderd. Een familie van modellen $f$ kan ook. Het probleem is dat het bij zulke lage compressie moeilijk is om een compressiemethode met een groot model te bedenken\ldots}

>>>>

\newcommand{\sdr}[1]{\textcolor{blue}{\small #1\textsuperscript{[Steven]} }}
\newcommand{\pb}[1]{\textcolor{OliveGreen}{\small #1 \textsuperscript{[Peter]} }}

@@

\section{Unbounded and top-heavy sophistications}

\begin{definition}
We call a version of Sophistication $F^\phi$ \emph{bounded} if its ad-hoc choices (the enumeration $\phi$) can be chosen so that
\[
	\exists c \forall x: F^\phi(x) \leq c \p
\]
Similarly, we call $F^\phi(x)$ \emph{top-heavy} if there exists a $\phi_1, \phi_2, \ldots$ such that
\[
	\exists c \forall x: F^\phi(x) \geq K^F(x) - c 
\]
Where $K^F$ is the two-part coding minimized within $F$.
\end{definition}

If some $F$ is either top-heavy, or unbounded we can show that it must either lack invariance, or be useless as a measure of model complexity. If the property proved holds for all enumerations $\phi$, and not just a single one, the sophistication is either bounded, or the same as the Kolmogorov complexity. If the measure is not bounded or top-heavy for other enumerations, the difference between the two is unbounded, and $F$ is not invariant.

One of the earliest proposals to separate structure and content was the Kolmogorov structure function \cite{TODO}. The following is the version of sophistication it leads to. 
\begin{definition}
\[
	S^\phi(x) = K(S^*) \,\tn{where }\, (S, i) = \argmin_{(S, i)\,:\,\text{$S$ is a finite set},\,S_i = x} K(S) + |i|
\]
\end{definition}

\begin{theorem}
There exist acceptable numberings $\phi_1, \phi_2, \ldots$ for which $S^\phi$ is top-heavy.
\end{theorem}
\begin{proof}
Let $\psi_1, \psi_2, \ldots$ be some acceptable numbering. Define $\psi$ as 
\begin{align*}
\phi_{0\bar\imath p}(\epsilon) &= \{\psi_i(p)\} \\
\phi_{1ri}(p) &= \psi_i(p)\\ 
\phi_j(x) = \infty \,\text{if $j$ cannot be decoded as above}
\end{align*}
For any $x$ with $\psi$-description $(i, p)$, that is is $\psi_i(p) = x$, we have two representations in $\phi$. Firstly, we have $\{x\}, 1$ with description length $K^\psi(x) + 2$. Secondly, we have a representation in $K^\psi{x} + r$. By choosing $r$ sufficiently large, the first representation will always win.
\end{proof}

\section{Vitanyi's Sophistication}

@@

\noindent \pb{Ik denk dat we dit kunnen bewijzen, maar het leidt uiteindelijk maar tot een logterm variantie tussen verschillende versies van G. Dat betekent dat ze asymptotisch niet echt verschillen. Wat we nodig hebben is een groot model $f$ waarvan we weten dat er een $x$ in $B^n$ zit, die met $f$ $C(x)$ to op een constante benaderd. Een familie van modellen $f$ kan ook. Het probleem is dat het bij zulke lage compressie moeilijk is om een compressiemethode met een groot model te bedenken\ldots}
